Refinements for open automata

### 2022-06-08 2021-Refinement/paper/refinementarticle.tex
proof sketch composition

\TODO{To discuss the following:} 
\item The last formula we need to prove is that the relation is preserved along identical transitions, i.e. the following is satisfied  $\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$ and
\begin{multline*}
 \bigsymb{\forall} \mpar{t_{13}, t_{23}} = \mpar{\OTx{13}{}{13}{13}, \OTx{23}{}{23}{23}} \in \fOT{s_{13}} \times \fOT{s_{23}} \\  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} \vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} \wedge \bigwedge_\subbox{j \in J'_{13} \cap J'_{23}} \beta_{13j} = \beta_{23j} \implies  R'\mpar{s'_{13}, s'_{23}}\psubst{\psi_{13} \uplus \psi_{23}}\\
\end{multline*}

>>>>

\item The last formula we need to prove is that the relation is preserved along identical transitions, i.e. the following is satisfied 
\TODO{NEW PROOF SKETCH}
HYPOTHESES and OBJECTIVES

TWO cases for the OT $t_{23}$

CASE 1 : $k$ does not move in $A_2$

two cases for  $t_{13}$

 ...

in both cases relation is preserved along identical transitions applied on A1 vs A2 provides a $t_{1}'$ such that HOLE $k$ does not move

and has the desired property for ``relation is preserved along identical transitions''

CASE 2 : k moves in $A_2$ with action $\beta_{2 k}$, and $A_3$ does the labelled action $\beta_{2 k}$.

two cases for  $t_{13}$

 ...

in both cases relation is preserved along identical transitions applied on A1 vs A2 provides a $t_{1}'$ such that HOLE $k$ should move with the action $\beta_{2 k}$.

We recompose a $t_{1}'$ with $t_{1}'$ and $t_3$ from  $t_{23}$

it has the desired property for ``relation is preserved along identical transitions''

relation on guards should hold but to be formulated carefully.

\TODO{END OF NEW PROOF SKETCH}
 $\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$ and
\begin{multline*}
 \bigsymb{\forall} \mpar{t_{13}, t_{23}} = \mpar{\OTx{13}{}{13}{13}, \OTx{23}{}{23}{23}} \in \fOT{s_{13}} \times \fOT{s_{23}} \\  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} \vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} \wedge \bigwedge_\subbox{j \in J'_{13} \cap J'_{23}} \beta_{13j} = \beta_{23j} \implies  R'\mpar{s'_{13}, s'_{23}}\psubst{\psi_{13} \uplus \psi_{23}}\\
\end{multline*}
